How to Avoid OOTA Without Really Trying

### 2024-10-02 paper/ootavacuous.tex
ootavacuous: x<->y in 2.1 to align with Listing 1
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

\emph{Tagline: ``Semantic dependencies are more complicated than you think.''}

@@

This is a fine definition and is consistent with the words in the C++
standard, but it has a problem with intrathread rfi links
as exemplified by the following code: \\
% \begin{quote}
% Constructed by hand.
{
\small
\begin{tabular}{r|l}
% & \multicolumn{1}{c}{T0} \\
% \hline
1. &
\texttt{~~int r2 = x} \\
2. &
\texttt{~~y = r2} \\
3. &
\texttt{~~int r3 = y} \\
4. &
\texttt{~~z = r3} \\
\end{tabular}
} \\
% \end{quote}
This is an elaboration of T1 from
Listing~\ref{lst:Simple OOTA}
that adds \co{z} along with lines~3 and~4.
The problem is that a C++ implementation may
note that line~3 could well execute immediately after line~2, giving
other threads no chance to modify \co{y} in between.
Such an implementation might therefore behave as if line~3 had been
removed from the source code and line~4's \co{r3} had been replaced by
\co{r2},
causing line~4 always to store the same value to \co{z} as was stored
to \co{y} by line~2.
And since the load from \co{y} has been removed, it cannot possibly
act as a temporal constraint.

>>>>

@@

This is a fine definition and is consistent with the words in the C++
standard, but it has a problem with intrathread rfi links
as exemplified by the following code: \\
% \begin{quote}
% Constructed by hand.
{
\small
\begin{tabular}{r|l}
% & \multicolumn{1}{c}{T0} \\
% \hline
1. &
\texttt{~~int r2 = y} \\
2. &
\texttt{~~x = r2} \\
3. &
\texttt{~~int r3 = x} \\
4. &
\texttt{~~z = r3} \\
\end{tabular}
} \\
% \end{quote}
This is an elaboration of T1 from
Listing~\ref{lst:Simple OOTA}
that adds \co{z} along with lines~3 and~4.
The problem is that a C++ implementation may
note that line~3 could well execute immediately after line~2, giving
other threads no chance to modify \co{x} in between.
Such an implementation might therefore behave as if line~3 had been
removed from the source code and line~4's \co{r3} had been replaced by
\co{r2},
causing line~4 always to store the same value to \co{z} as was stored
to \co{x} by line~2.
And since the load from \co{x} has been removed, it cannot possibly
act as a temporal constraint.
